\papertitle

### 2014-03-18 final-report/paper.tex
more info

Our goal is to build a visualization tool designed to help a database administrator understand the data flow and run-time
performance during query execution in a Distributed Database Management System (DDBMS). Using our tool, the
database programmer or administrator could quickly discover run-time bottlenecks as well as problematic data skew issues, 
saving them significant guesswork and programming effort to identify the appropriate logs to analyze. Our visualization tool
is called \system, which uses profiling logs from Myria \cite{myria} as the prototype DDMS. Myria is a distributed 
database platform that provides \emph{big data management and analytics as a service} primarily for scientific applications.
Myria takes queries in high-level query languages, such as SQL, translating them into physical query plans and finally executing
them in parallel. Currently

@@

\begin{itemize}
    \item problem: hard to learn why a query is slow
    \item motivation: help developers/programmers dig what the problems might be
    \item Questions: find data/execution skew, identify performance bottlenecks, visualize data flow in the system (elaborate on each point)...
\end{itemize}

>>>>

Our goal is to build a visualization tool designed to help a database administrator understand the data flow and run-time
performance during query execution in a Distributed Database Management System (DDBMS). Using our tool, the
database programmer or administrator could quickly discover run-time bottlenecks as well as problematic data skew issues, 
saving them significant guesswork and programming effort to identify the appropriate logs to analyze. Our visualization tool
is called \system, which uses profiling logs from Myria \cite{myria} as the prototype DDMS. Myria is a distributed 
database platform that provides \emph{big data management and analytics as a service} primarily for scientific applications.
Myria takes queries in high-level query languages, such as SQL, translating them into physical query plans and finally executing
them in parallel. Currently, Myria does not offer a visualization tool designed to show the physical query plan, job execution and network 
communication between distributed workers. \system allows the programmer/database administrator to visualize the following aspects
of query execution.

\begin{itemize}

\item An interactive visualization of the physical query plan. The physical query plan in Myria is composed of
a DAG of fragments, where each DAG link represents communication between workers, possibly over the network. 
\system displays this DAG in an interactive fashion with clickable elements for fragment nodes and communication links. 
This DAG also represents a high-level data flow in the DDBMS.

@@

% \item Questions: find data/execution skew, identify performance bottlenecks, visualize data flow in the system (elaborate on each point)...
